Market-based Mechanisms for Resource Scheduling

### 2013-12-17 paper/paper.tex

\subsection{Performance With Pricing}

>>>>

\subsection{Performance With Pricing\\}

When pricing information is provided, we show that the market-based mechanism can provide better performance than in DRF. As discussed in Section TODO, there are many situations in which prices can be used to better encapsulate a framework's preferences. As a case study, we investigate one particular scenario of inhomogeneous performing resources.

In this case, we assume certain nodes have a special resource that significantly improves job performances, while the remaining nodes do not. In a realistic case, this special resource could be a GPU, which can significantly reduce CPU-bounded job completion times. While most jobs will see some performance benefits from running on a GPU, some jobs may be specifically crafted for optimal performance on a GPU, and hence will see the largest performance improvement if run on a GPU.

The current Mesos implementation does not recognize this special sort of inhomogeneous performing resource. However, if a framework is aware of the inhomogeneous performing resource, it can schedule tasks appropriately on slaves when offered, such that the tasks that benefit most from special resources will be scheduled on special resource slaves. For the simulations, we have implemented the framework scheduler in such a manner. For the market-based mechanism, we use a bidding policy proportional to the default bidding policy. However, when a task can benefit from a special slave by a speedup factor $s$, the default bid is multiplied by $\frac{1}{s}$, resulting in a bid that is inversely proportional to the speedup factor.

We simulate this scenario using a 64-node cluster, where 16 nodes have the special resource. Jobs from the statistical workload are uniformly randomly assigned one of two speedup factors, such that all tasks in a job experience the same speedup factor. The ``slow" speedup reduces task runtime by 10\%, while the ``fast" speedup reduces task runtime by 90\%. All tasks with a ``fast" speedup are marked as preferring a special resource slave, and a framework in DRF Mesos will schedule a ``fast" task on a special resource slave if possible. The workload was again generated for five frameworks, with up to 20 jobs running in parallel.

Figure JOB-COMPLETION depicts the time progression of job completions, where a job is considered finished when all of its tasks are finished. As the figure depicts, the market-based mechanism is consistently ahead of DRF at all times, and finishes all jobs in about 20\% less time than DRF. Looking in detail, we find that DRF schedules only 30\% of ``fast" tasks on special resource slaves, while the market-based mechanism schedules 60\%. One might note that around the eighth hour, it appears DRF catches up to the market-based mechanism before falling behind again. This effect is caused by a long running job that the market-based mechanism schedules earlier than DRF. Its completion progresses the fraction of job completion minimally yet accounts for a long period of time. This allows DRF, which is still completing earlier short-lived tasks, to momentarily catch up in the fraction of job completion. When DRF schedules the same long-lived job at a latter point, it once again lags behind the market-based mechanism.

Hence, in the case of inhomogeneous performing resources, the market-based mechanism can allow frameworks to better express their preferences than DRF, resulting in better performance for the market-based mechanism. DRF only allows a framework to specifically target special resource slaves when the framework is offered, whereas the market-based mechanism allows frameworks who benefit most from a special resource slave to outbid others. By better scheduling jobs on machines that best complete them, we see the overall performance improvements of the market-based mechanism.
